Review of Assigned Readings

### 2018-01-04 paper/paper.tex
Update paper.tex

\subsection{Stationarity}
Before estimating a VAR model, the time series data's stationarity must be confirmed. Namely, we need to demonstrate that the means and variances are constant over time, and that the dataset does not show any trending behavior. Non-stationary data can lead to an inaccurate estimation with VAR model. To conduct stationarity test, we use the Augmented Dickey-Fuller (ADF) test.\\

@@

Once again, the test result suggests we use the first difference transformation of the variable bitcoin prices, for stationarity to be fulfilled.

\subsection{Lag-Specification}
To select the optimal number of lags to use for the VAR regression, we have to check for various information criteria. Information criteria are measuring the tradeoff between model fit and parsimony, giving the optimal number of lags to use (\cite[p.~27]{brandtwilliams2007}). The calculations of these criteria for our specific data set are shown in the following table.\\

@@

As can be seen, STATA calculates and presents various information criteria (AIC, HQIC, SBIC). The asterisk indicates the optimal lag lenght to use for the regression analysis. In this case all criteria suggest a lag length of 1.

>>>>

\subsection{Preparing for VAR: Stationarity Test}
Before estimating a VAR model, the time series data's stationarity must be confirmed. Namely, we need to demonstrate that the means and variances are constant over time, and that the dataset does not show any trending behavior. Non-stationary data can lead to an inaccurate estimation with VAR model. To conduct stationarity test, we use the Augmented Dickey-Fuller (ADF) test.\\

@@

Once again, the test result suggests we use the first difference transformation of the variable bitcoin prices, for it succeeds best the ADF test.

\subsection{Preparing for VAR: Lag-Specification}
To select the optimal number of lags to use for the VAR regression, we have to check for various information criteria. Information criteria measure the tradeoff between model fit and parsimony, giving the optimal number of lags to use (\cite[p.~27]{brandtwilliams2007}). The calculations of these criteria for our specific data set are shown in the following table.\\

@@

As can be seen, STATA calculates and presents various information criteria (AIC: Akaike Information Criterion, HQIC: Hannan–Quinn information criterion, SBIC: Schwarz-Bayesian Information Criterion). The asterisk indicates the optimal lag lenght to use for the regression analysis. In this case all criteria suggest a lag length of 1.
